---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# verbformen

<!-- badges: start -->
<!-- badges: end -->

The goal of verbformen is to query the website [verbformen.de](https://www.verbformen.de/) for *Konjugationen* (conjugations, derived forms of a verb) and *Deklinationen* (declensions, different forms of a noun or an adjective) of a German word. Additional data are also provided (e.g. whether the verb is seperable). The data is provided with the [CC BY-SA 4.0](https://creativecommons.org/licenses/by-sa/4.0/) License. The copyright holder of the data is Netzverb® Deutsch. Please share the data with the same license and an appropriate attribution. More information is available in the [Nutzungsbedingungen](https://www.netzverb.de/impressum.htm) of the website.

## Installation

You can install the GitHub version of verbformen with:

``` r
devtools::install_github("chainsawriot/verbformen")
```

## Example

Query verbformen.de. Please note that the query does not need to be in the *Grundform*. For example, querying *bin* (no need to be *sein*):

```{r example}
library(verbformen)
verbformen("bin")
```

If you don't need those additional information, you can get a tibble in the tidy format using the argument `tidy`.

```{r tidy}
verbformen("aufgegeben", tidy = TRUE)
```

You can also tidy the object after a query.

```{r anotherway}
x <- verbformen("befinden")
x
tidy(x)
```
